
\parindent 0in
\parskip 0.1in

\begin{center}
{\bf Benefits of Collaboration } \\
{\it  Reduced Order Modeling of heat and fluid flow: Multi-scale modeling of advanced reactors to enable faster deployment }
\end{center}

The collaborative team assembled for the proposed work consists of nuclear engineers, mechanical engineers and computer scientists.  The collaborators cover the entire spectrum of knowledge necessary to pursue the proposed work.

\section{Principal Investigators: Short Biographies}
\begin{itemize}
\item \textit{Paul Fischer} (UIUC) ...
\item \textit{Elia Merzari} (PSU), is an Associate professor in nuclear engineering and associate editor of Nuclear Engineering and Design, and previously held various leadership
roles as a principal nuclear engineer at Argonne National Laboratory (ANL). His expertise spans nuclear engineering multi-physics applications , high-performance computing, and CFD simulations, reduced order models as well as NEUP-funded nuclear engineering work. He has worked on Proper Orthogonal Decomposition, a key method for this proposal for 15 years.
\item \textit{Dillon Shaver} (ANL) is a Principal Nuclear Engineer in the Nuclear Science and Engineering Division at Argonne National Laboratory, and responsible for the high fidelity thermal-hydraulic simulation in the Nuclear Energy Advanced Modeling and Simulation (NEAMS) program. He has worked extensively in the area of Computational Fluid Dynamics and he has been instrumental in developing multiphase and Reynolds Averaged Navier Stokes models in Nek5000. He has broad experience in the use of high fidelity models in the advanced reactor industry.
\end{itemize}
\section{Principal Investigators: Interaction and Responsibilities}
The team will meet every two-weeks to coordinate on different development aspects of the project. Detailed work on specific models will be developed by each co-PI together with the graduate students who will be supported by this project. Each collaborating person/institution contributes a complementary set of expertise, and their responsibilities will be as follows:
\begin{itemize}
    \item \textit{Paul  Fischer} will  lead the overall project and ensure a smooth and productive interaction among all areas. He will also lead overall algorithmic development with a focus on order reduction.
    \item \textit{Elia  Merzari} will lead the high fidelity simulation thrust for Large Eddy SImulation (LES) and Direct Numerical Simulation (DNS) datasets in rod bundles as well as the validation, testing and demonstration thrust. He will also support algorithmic development by focusing on the interaction between high fidelity and the reduced order models.
    \item \textit{Dillon Shaver} will support ongoing efforts by consulting on the relevance to the NEAMS program and the advanced reactor industry.
\end{itemize}
\section{Synergistic Acitvities}
The work will also have a direct impact on NEAMS, with applications of direct relevance to the nuclear industry, and indirectly to other DOE applications that rely on fluid flow and heat transfer.The project has the potential to enable a transformative change in the way thermal-hydraulic simulations are performed.

Elia Merzari is currently leading a NEAMS IRP developing a multiscale framework capable of using high-resolution simulation data to improve low-order models through better closures. This effort ties into the proposed work, and lessons learned from that effort will be leveraged as it is a natural evolution of that work.

The PIs are active in the nuclear thermal-hydraulics community and the American Nuclear Society in particular (e.g., Elia Merzari is the immediate past chair of the thermal-hydraulic division and Dillon Shaver is the current Program chair). Results from the project will be disseminated in conferences, special sessions and journal articles.


\section{Facilities}
The proposed computational work will be performed at various high performance computing facilities, where the PIs already have awarded allocations.

The co-PI at Penn State has an allocation at the local ROAR supercomputer that will be leveraged for both testing and optimization simulations. ROAR is Penn State’s flagship research cluster maintained by ICDS. Roar includes basic, standard, and high memory compute as well as GPU processors. ROAR operates more than 30,000
Basic, Standard and High Memory cores to support Penn State research. The system provides dual 10- or 12-core Xeon E5-2680 processors for Basic and Standard memory configurations and quad 10-core Xeon E7-4830 processors for High Memory configurations. In addition to access to ROAR, request for allocations with DOE’s ALCC and INCITE programs will be submitted for access to DOE’s supercomputing facilities if needed. Access to INL Sawtooth will also be pursued.
%
% {\bf D.2 Benefit of Collaboration} (4 pages)
%
% Applicant shall provide a narrative that includes an explanation of the
% contribution that will be made by the collaborating organizations and/or
% facilities to be utilized. It may contain brief biographies of staff and
% descriptions of the facilities wherein the research will be conducted. Please
% indicate within this section whether the application has benefit or influence
% on other ongoing or proposed NE R\&D projects (e.g., modeling and simulation in
% one application and effect validation in a separate application).
%
% This document is required unless the application only has a single principal
% investigator.
%
% Pages outside the specified page limits and font size, including references,
% will be redacted and unavailable for evaluators to review.
%
% o 4-page limit, 11-point font.
%
% Name File: 2023 RPA Benefit of Collaboration “Insert ID \#”
