
\vspace{.08in}
\noindent \textbf{Coupled Multiscale Simulations} (Tasks 2 and 3.)
The goal of this task is to reduce computational costs by using ROMs in 
combination with other computational fluid dynamics and thermal-hydraulic
approaches. We note that ROMs can be readily used in the context of systems
analysis codes. We will demonstrate this within the context of the recently
developed SAM-NekRS coupling in Cardinal.

ROMs can replace the solution of the Navier-Stokes equations with a simplified
model, which can greatly reduce computational time. However, some parts of the
domain may require additional resolution. Therefore, we will examine hybrid
LES-ROM models, which combine a ROM model for the entire system or assembly
with a localized, more detailed LES model for specific regions.
Fig.~\ref{fig:cha1}(right) illustrates a proposed example of an assembly solved
using a ROM with four subchannels near a thimble solved using wall-resolved LES
for detailed heat transfer.  The modal decomposition of the ROM can readily
provide the flow boundary conditions for the LES.  For small LES domains, a
one-way approach where information flows only from the ROM to the LES may be
sufficient. If the flow behavior within the LES domain is expected to have a
global impact, a two-way coupling approach is needed. We will focus on an
overlapping domain approach where the LES behavior is translated into forcing
terms for each mode of the ROM.

We will also examine RANS-ROM modeling as a potential interface for ROM
methods. This includes using previous work on rod bundles and sub-channels,
where high-fidelity simulation was used to improve RANS results
\cite{martinez2019a}.
Our aim is to develop a generalized interface between RANS and ROM. For
example, ROM results from one assembly can be superposed over a transient RANS
model of the entire system to recover unsteady features not modeled correctly
by RANS. To this end, it is crucial to ensure that the energy transfer between
scales is realistic. We will leverage recent work on the concept of a novel
energy-based ROM length scale \cite{mou2021}. We will also explore the
potential of an uplifting ROM approach \cite{ahmed2020} where closure and
projection errors are corrected in the prolongation to RANS.
\\[-2ex]

